% ************************** Thesis Acknowledgements **************************

\begin{acknowledgements}      

Without the effort of several people this work wouldn't be possible. First of all, I would like to thank my supervisor, Marco Di Natale, for having introduced me into the world of the Model-Based Design, for being always available to answer my questions and clarify my doubts and, most important, for his precious life teachings.

\paragraph{} I would like to thank United Technologies Research Center for the big opportunity they gave to me. In this six months I experienced a professional and high qualified environment. I have been really surprised on how employees are considered to be the most important resource to achieve their purposes. A special thank to Vassilios Tsachouridis who really made me capable to deal with the complexity of Control Systems. I consider myself very lucky for having worked with him. Thank also to Stylianos Basagiannis who always watched over me and ensured of my wellness. Lastly, thank to the rest of the team, Juan Valverde and Georgeos Giantamidis for the hard work and the funny moments.

\paragraph{} I would like to mention also people who indirectly contributed to this work.
\\
\textit{Un ringraziamento speciale ai miei amici per non avermi mai fatto mancare il loro aiuto, con le parole e, soprattutto, con i fatti. Senza il contributo di ciascuno di voi non sarei arrivato a questo traguardo.
\\
Grazie a Miriam per essermi stata accanto in questi anni, per avermi sopportato e avermi sempre offerto una via di fuga dai miei pensieri.
\\
Infine, grazie alla mia famiglia per non avermi mai fatto mancare il loro supporto e la loro fiducia.}

{\raggedleft\vfill\itshape\Longstack[l]{
  Marco Celia\\
  Cork, July 2017
}\par
}


\end{acknowledgements}
